On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2023-07-18 Manuscript/manuscript.tex
Updated tables and moved Seiko to Discussion, still need to make it fit

\jy{label the table and reference to it; clean it up}
\begin{table}
  \centering
  \caption{Probabilities of observing reaction times less than 0.1, 0.08, and
  0.08 for various data sets.}
  \begin{tabular}{c c c} 
   \toprule
   Data Set & P(RxnTime $<$ 0.1) & P(RxnTime $<$ 0.08) \\ 
   \midrule
   Old Finals & $4.39\cdot10^{-4}$ & $2.0\cdot10^{-5}$ \\
   All Finals & $8.56\cdot10^{-4}$ & $6.0\cdot10^{-7}$ \\
   Old Pooled & $5.76\cdot10^{-3}$ & $1.0\cdot10^{-4}$ \\ 
   All Pooled & $6.86\cdot10^{-3}$ & $1.3\cdot10^{-4}$ \\
   \bottomrule
  \end{tabular}
  \label{tab:Sim_probability}
\end{table}

\begin{table}
  \centering
  \caption{Suggested reaction time barriers based on probability of observing
  a time less the barrier. \of{Not sure if this makes sense}}
  \begin{tabular}{c c c} 
   \toprule
   Data Set & P(RxnTime $<$ x = .001) & P(RxnTime $<$ x = 0.0001) \\ 
   \midrule
   Old Finals & $0.103$ & $0.095$ \\
   All Finals & $0.101$ & $0.093$ \\
   Old Pooled & $0.090$ & $0.080$ \\ 
   All Pooled & $0.089$ & $0.079$ \\
   \bottomrule
  \end{tabular}
  \label{tab:Sim_time}
\end{table}

@@

%Citation needed in this section
Since 1985 Seiko Holding Corporations has served every World Athletics 
Championships as the official timer \citep{wa2022seiko}.  Since 1985, the 
technology and the ability
to accurately predict measurements: long jump distances, false starts, total 
time, reaction time, etc. have all dramatically improved.  Seiko did not start 
tracking reaction time as an official measurement until 1999 in the men's 110 meter
hurdles and women's 100 meter hurdles. 
Seiko regularly updates their equipment so that they provide cutting edge
technology to the World Track and Field Championships, the highest stakes in the 
world of running outside of the Olympics. Seiko's technology for detecting 
reaction times relies on the pressure that athletes exert on the plate when they 
push off.  Their systems measure the time differential
between when the ``gun" goes off to start the race and when the pressure changes 
\citep{wa2022seiko}.  If an athlete has a reaction time under 0.1 seconds, it 
is deemed a 
false start as it is considered that no athlete can react so quickly 
\citep{Seiko-Timing}.  Thus, a reaction time of for example 0.05, suggests that 
the athlete predicted the gun and it was luck that caused their abnormally high 
time.  At the World Championships level, World Athletics and Seiko want to remove 
that element of luck and thus impose the 0.1 second barrier. In 2013, Seiko 
upgraded their timing equipment for sprinting events (110 meter hurdles falls 
under this category) \citep{wa2013backtage}. Since 1999, the
slowest reaction 
times in the men's 110-meter hurdle were recorded in 2013.  That is not to say
 that the higher 
times were caused by Seiko's equipment, but the two may be related.  It is worth 
noting that prior
to 2022, Seiko again upgraded its technology but for its jump management system.
\eds{I would argue that this paragraph should go in the discussion as there are 
no results presented here}

@@

	The rank based methods described in Section~\ref{sec:rank} are used
to determine if the reaction times for athletes who had competed at other 
championships differed significantly from the 2022 World Championships. 
\jy{Remind the readers what the analysis was about: two-group comparison with
  group being ....}

\subsubsection{2019 World Track and Field Championships} \label{sec:results2019vs2022}
 We can
use the 2019 World Championships and the 2022 national-level championships as a 
precedent to see how athletes performance changed across different championships.

When the clusrank rank sum test was performed, the ``ds" method produced a z score of
2.9751 and p value of 0.001464.  \eds{what is the ds method?} 
This value is for a one-sided test and show that
the mean reaction time on average in 2019 was larger (slower) than the mean 
reaction time
in 2022 for athletes who competed in both championships at an alpha level of 0.01.
This provides good evidence that athletes who competed in both 2019 and 2022 got
faster during that timespan.  \eds{That is not the only explanation}
\subsubsection{2022 National Championships} \label{sec:resultsnational}

@@

>>>>

\jy{label the table and reference to it; clean it up}
\begin{table}
  \centering
  \caption{Probabilities of observing reaction times less than 0.1, 0.08, and
  0.08 for various data sets.}
  \begin{tabular}{c c c} 
   \toprule
   Data Set & P(RxnTime $<$ 0.1) & P(RxnTime $<$ 0.08) \\ 
   \midrule
   Old Finals & $4.36\cdot10^{-4}$ & $3.0\cdot10^{-7}$ \\
   All Finals & $8.64\cdot10^{-4}$ & $6.0\cdot10^{-7}$ \\
   Old Pooled & $4.15\cdot10^{-3}$ & $4.67\cdot10^{-5}$ \\ 
   All Pooled & $5.15\cdot10^{-3}$ & $6.01\cdot10^{-5}$ \\
   \bottomrule
  \end{tabular}
  \label{tab:Sim_probability}
\end{table}

\begin{table}
  \centering
  \caption{Suggested reaction time barriers based on probability of observing
  a time less the barrier. \of{Not sure if this makes sense}}
  \begin{tabular}{c c c} 
   \toprule
   Data Set & P(RxnTime $<$ x = .001) & P(RxnTime $<$ x = 0.0001) \\ 
   \midrule
   Old Finals & $0.103$ & $0.095$ \\
   All Finals & $0.101$ & $0.093$ \\
   Old Pooled & $0.093$ & $0.083$ \\ 
   All Pooled & $0.091$ & $0.082$ \\
   \bottomrule
  \end{tabular}
  \label{tab:Sim_time}
\end{table}

@@

@@

The rank based methods described in Section~\ref{sec:rank} are used
to determine if the reaction times for athletes who had competed at other 
championships differed significantly from the 2022 World Championships.  This is
a two group comparison performed two times: once comparing 2019 World
Championships to 2022 World Championships and can be found in 
section~\ref{sec:results2019vs2022} and secondly comparing 2022 national
championships to the 2022 World Championships and can be found in 
~section\ref{sec:resultsnational}.
\jy{Remind the readers what the analysis was about: two-group comparison with
  group being ....}

\subsubsection{2019 World Track and Field Championships} \label{sec:results2019vs2022}
The p value associated with the two group comparison for 2019 and 2022 was 0.001464.  
\eds{what is the ds method?} \of{Its described in the methods section but I dont
think its no longer needed now that we are no longer using the other grouping
method (I believe it was called something like the rosner method)}
This value is for a one-sided test and show that
the mean reaction time on average in 2019 was larger (slower) than the mean 
reaction time
in 2022 for athletes who competed in both championships at an alpha level of 0.01.
This provides good evidence that athletes who competed in both 2019 and 2022 got
faster during that timespan.  \eds{That is not the only explanation}
\subsubsection{2022 National Championships} \label{sec:resultsnational}

@@

Since 1985 Seiko Holding Corporations has served every World Athletics 
Championships as the official timer \citep{wa2022seiko}.  Since 1985, the 
technology and the ability
to accurately predict measurements: long jump distances, false starts, total 
time, reaction time, etc. have all dramatically improved.  Seiko did not start 
tracking reaction time as an official measurement until 1999 in the men's 110 meter
hurdles and women's 100 meter hurdles. 
Seiko regularly updates their equipment so that they provide cutting edge
technology to the World Track and Field Championships, the highest stakes in the 
world of running outside of the Olympics. Seiko's technology for detecting 
reaction times relies on the pressure that athletes exert on the plate when they 
push off.  Their systems measure the time differential
between when the ``gun" goes off to start the race and when the pressure changes 
\citep{wa2022seiko}.  If an athlete has a reaction time under 0.1 seconds, it 
is deemed a 
false start as it is considered that no athlete can react so quickly 
\citep{Seiko-Timing}.  Thus, a reaction time of for example 0.05, suggests that 
the athlete predicted the gun and it was luck that caused their abnormally high 
time.  At the World Championships level, World Athletics and Seiko want to remove 
that element of luck and thus impose the 0.1 second barrier. In 2013, Seiko 
upgraded their timing equipment for sprinting events (110 meter hurdles falls 
under this category) \citep{wa2013backtage}. Since 1999, the
slowest reaction 
times in the men's 110-meter hurdle were recorded in 2013.  That is not to say
 that the higher 
times were caused by Seiko's equipment, but the two may be related.  It is worth 
noting that prior
to 2022, Seiko again upgraded its technology but for its jump management system.
\eds{I would argue that this paragraph should go in the discussion as there are 
no results presented here}
